Historical aerial surveys map long-term changes of forest cover and structure in the central Congo Basin

### 2019-12-30 manuscript/appendix.Rmd
CNN stats and plot of Geo-Eye panchrom image

ct <- crosstab(m, loss)
ct <- round(ct/sum(ct),2)
rownames(ct) <- c("non-forest","forest")

ct %>%
   kable(
    caption="Contingency table between the two forest / non-forest maps generated from a Geo-Eye 1 pan-chromatic image using a Convolutional Neural Network (CNN) generated and the Global Forest Cover map (Hansen et al. 2013).",
    booktabs = TRUE,
    col.names =  c("non-forest","forest")) %>%
  add_header_above(c("CNN" = 1, "Global Forest Cover" = 2)) %>%
  kable_styling(latex_options = c("hold_position"))

>>>>

ct <- crosstab(m, loss)
ct <- round(ct/sum(ct),2) * 100
rownames(ct) <- c("non-forest","forest")

ct %>%
   kable(
    caption="Contingency table in agreement (%) between forest / non-forest classes as generated from a Geo-Eye 1 pan-chromatic image using a Convolutional Neural Network (CNN) generated and the Global Forest Cover map (Hansen et al. 2013).",
    booktabs = TRUE,
    col.names =  c("non-forest","forest")) %>%
  add_header_above(c("CNN" = 1, "Global Forest Cover" = 2)) %>%
  kable_styling(latex_options = c("hold_position"))

### 2019-12-30 manuscript/appendix.tex
CNN stats and plot of Geo-Eye panchrom image

\caption{\label{tab:unnamed-chunk-10}Contingency table between the two forest / non-forest maps generated from a Geo-Eye 1 pan-chromatic image using a Convolutional Neural Network (CNN) generated and the Global Forest Cover map (Hansen et al. 2013).}
\centering
\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{CNN} & \multicolumn{2}{c}{Global Forest Cover} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-3}
  & non-forest & forest\\
\midrule
non-forest & 0.10 & 0.09\\
forest & 0.04 & 0.77\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\textbackslash{}begin\{table\}{[}!h{]}

\textbackslash{}caption\{\label{tab:unnamed-chunk-10}Contingency table
in agreement (\%) between forest / non-forest classes as generated from
a Geo-Eye 1 pan-chromatic image using a Convolutional Neural Network
(CNN) generated and the Global Forest Cover map (Hansen et al.~2013).\}
\centering

\begin{tabular}[t]{lrr}
\toprule
\multicolumn{1}{c}{CNN} & \multicolumn{2}{c}{Global Forest Cover} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-3}
  & non-forest & forest\\
\midrule
non-forest & 10 & 9\\
forest & 4 & 77\\
\bottomrule
\end{tabular}

\textbackslash{}end\{table\}
